\centerline{\bf ÖZET}
\addcontentsline{toc}{section}{ÖZET}

\begin{center}
\textbf{Projenin Amacý}
\end{center}
\qquad Bu proje sayesinde  mühendislik ve teknik eðitimde sýkça kullanýlan MATLAB uygulamasýnýn Web tabanlý olarak gerçekleþtirilmesi hedeflenmiþtir. Web sayfasýnda File Upload iþlemi yaparak seçtiðimiz resim Matlab'a gönderilir.  Görüntü iþleme ile resimdeki kiþi sayýsý bulunur. Ardýndan kiþi sayýsý  Web'de yazdýrýlýr. 
\begin{center}
\textbf{Projenin Kapsamý}
\end{center}
\qquad Matlab uygulamasý olarak günümüz de yaygýn olan görüntü iþleme esas alýnmýþtýr. Görüntü Ýþlemenin çok çeþitli ve farklý uygulamalarý olmakla birlikte görüntü iþleme, pek çok alanda kullanýlmaktadýr. Söz konusu yoðun kullaným alanlarýnýn internet üzerinde icra edilmesi ile görüntü iþleme kapsamýnda web tabanlý çeþitli proje, çalýþma ve araþtýrma gibi uygulamalar gerçekleþtirilebilir. Ayrýca arayüzün web tabanlý tasarlanmasýyla, yöntemin yaygýnlaþtýrýlmasý, zaman kaybýný ortadan kaldýrarak birden fazla kullanýcýnýn eþ zamanlý kullanabilmesi amaçlanmýþtýr.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%ABSTRACT%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\centerline{\bf ABSTRACT}
\addcontentsline{toc}{section}{ABSTRACT}
\begin{center}
\textbf{Project Objective}
\end{center}

 Thanks to this project has been targeted frequently used in education of engineering and technical realization as a Web-based MATLAB applications. File Web page 
choose Upload making process images sent to MATLAB. The number of people located in the picture with the image processing. Then the number of people is printed on the web[5].


%Bilecik Þeyh Edebali University Department of Computer Engineering students is studied. The aim of project is work to create a template for writing \LaTeX\ writing the final report template in the Project, to be written.

\begin{center}
\textbf{Scope of Project}
\end{center}
\qquad Today as Matlab image processing applications have also been widespread basis. While a variety of different image processing and image processing applications, however, are used in many fields. Said intensive use of the area covered by the image processing to be carried out on the internet with various web-based projects, such as studies and research carried out applications. In addition, by designing the web-based interface, dissemination methods, eliminating the time-consuming aimed multiple users can use simultaneously[5].


%Bilecik Þeyh Edebali University Computer Engineering Department Bilecik need to create a project template Latex codes assignment, involves the use of. The first part of the project consists of two parts, \LaTeX's development have been studied and why it is preferred that the use of information provided in the information. Faculty of Engineering of the university for the second part, Sheikh Edebali Bilecik Project Paper \LaTeX\ codes and are included.

